---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# midi

JUST A DRAFT!!!

This is a rewrite of `TuneR::readMidi()`, with a counterpart to write midi.

We don't create a data.frame but a list.

It should probably be an R6 object, and the structure should evolve.

I'd like to be able to change scales/modes, apply arpeggios etc, maybe do some
analysis on big amounts of midi files to detect patterns in styles of music or
specific artists, but we're far from there.

I'd like to do the same with guitar pro files too.

## Installation

You can install the released version of midi from [CRAN](https://CRAN.R-project.org) with:

``` r
remotes::install_github("moodymudskipper/midi")
```

## Example

Load file (a single piano note), check out the parsed data, write it back and check that it is
the same. 

```{r}
library(midi)

file <- "data/test.mid"

parsed <- parse_midi(file)
str(parsed)

file2 <- tempfile(fileext = ".mid")
encode_midi(parsed, file2)

hexView::viewRaw(file)
hexView::viewRaw(file2)
```
