---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# midi

JUST A DRAFT!!!

This is a rewrite of `TuneR::readMidi()`, with a counterpart to write midi.

We don't create a data.frame but a R6 object.

It's still very brittle and changes frequently significantly.

I'd like to be able to change scales/modes, apply arpeggios etc, maybe do some
analysis on big amounts of midi files to detect patterns in styles of music or
specific artists, but we're far from there.

I'd like to do something similar with guitar pro files too as their structure is
more suited to songwriting and the gp5 file format has been reverse engineered.

## Installation

Install with:
``` r
remotes::install_github("moodymudskipper/midi")
```

## Example

Load a simple music file with 2 instruments (that's 3 tracks here) 

```{r}
library(midi)

mid <- midi$new("https://www.8notes.com/school/midi/violin/vivaldi_spring.mid")

# it prints nicely
mid

# we can show separately header or tracks
mid$header

# print names, tempo, key
mid$names
mid$tempo

# plot
mid$plot()

# re-encode to midi
local_file <- tempfile(fileext = ".mid")
mid$encode(local_file)

# and reimport to check if our back and forth transformation was reliable
mid_reimported <- parse_midi(local_file)
all.equal(mid, mid_reimported)
```

We can play one track or two in stereo, this is done by converting to wave,
directly inspired by David Solito's work 
(see https://www.davidsolito.com/post/midiplayer-avec-r-part-2/ ).

```{r, eval = FALSE}
mid$play("Piano","Violin")
```

We can also use `$cut()` to restrict the song to a time window, `$rename()` and `$select()` to manipulate tracks, `$set_tempo()` to assign a tempo,
`$shift_hstep()`to move all notes of chosen tracks by half steps or `$shift_degree`
to shift chosen tracks by a chosen interval on a chosen scale.

These modifications don't produce yet an obejct that one can re-encode back to midi,
but we can already use our `$play()` method on them.

Harmonize vivaldi :

```{r, eval = FALSE}
vivaldi_mid$
  # select Violin track twice (i.e. subset and duplicate)
  select(Violin1=Violin, Violin3=Violin)$
  # shift all notes by 2 intervals in A maj so Violin3 is the third of Violin1
  shift_degree(2, scale_major("a"), at = Violin3)$
  # play in the re
  play("Violin","Violin3")
```

